Methods for Large Scale Learning to Rank

### 2014-11-13 report/Chapters/Background.tex
meer Dolf

\subsection{Mean Average Precision}
\ac{AP} \cite{Zhu2004} is an often used binary relevance judgement based metric that can be seen as a trade-off between precision and recall that is defined as\\

@@

@@

\section{Approaches to Learning to Rank}
\label{sec:ltr_approaches}
\subsection{Pointwise Approach}
The pointwise approach can be seen as the most straightforward way of using machine learning for ranking. Pointwise Learning to Rank methods directly apply machine learning methods to the ranking problem by observing each document in isolation. They can be subdivided in the following approaches:
	\begin{enumerate}
	\item regression-based, which estimate the relevance of a considered document using a regression model.
	\item classification-based, which classify the relevance category of the document using a classification model.
	\item ordinal regression-based, which classify the relevance category of the document using a classification model in such a way that the order of relevance categories is taken into account. 
	\end{enumerate}
Well-known algorithms that belong to the pointwise approach include McRank \cite{Li2007} and PRank \cite{Crammer2001}.
\subsection{Pairwise Approach}
Pointwise Learning to Rank methods have the drawback that they optimise real valued expected relevance, while evaluation metrics like \ac{NDCG} and \ac{ERR} are only impacted by a change in expected relevance when that change impacts a pairwise preference. The pairwise approach solves this drawback of the pointwise approach by regarding ranking as pairwise classification.\\

>>>>

\subsection{Mean Average Precision}
\ac{AP} \cite{Zhu2004} is an often used binary relevance-judgement-based metric that can be seen as a trade-off between precision and recall that is defined as\\

@@

In this formula $Q$ is the number queries.

@@

\section{Approaches to Learning to Rank}
\label{sec:ltr_approaches}
\subsection{Pointwise Approach}
The pointwise approach can be seen as the most straightforward way of using machine learning for ranking. Pointwise Learning to Rank methods directly apply machine learning methods to the ranking problem by observing each document in isolation. They can be subdivided in the following approaches:
	\begin{enumerate}
	\item regression-based, which estimate the relevance of a considered document using a regression model.
	\item classification-based, which classify the relevance category of the document using a classification model.
	\item ordinal regression-based, which classify the relevance category of the document using a classification model in such a way that the order of relevance categories is taken into account. 
	\end{enumerate}
Well-known algorithms that belong to the pointwise approach include McRank \cite{Li2007} and PRank \cite{Crammer2001}.
\subsection{Pairwise Approach}
Pointwise Learning to Rank methods have the drawback that they optimise real-valued expected relevance, while evaluation metrics like \ac{NDCG} and \ac{ERR} are only impacted by a change in expected relevance when that change impacts a pairwise preference. The pairwise approach solves this drawback of the pointwise approach by regarding ranking as pairwise classification.\\
